Blockchain System

### 2021-01-19 papers/execution-model/model.tex
Merge Master

\begin{definition}%[Program]
\emph{Expressions} are defined by the following grammar:
\begin{align*}
  \CONSTANT & ::= \INT %\mid \ADDR
              \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\INT) \mid
            \STATUSTIMEOUT \\
  \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
           \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
  \EXPR \mid \SOME\ \EXPR \mid \NONE
  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
  \\&\mid \QOP\  \EXPR\\
  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
\end{align*}
We let $\EXPRS$ range over sets of expressions.

@@

\begin{definition}%[Contractor]
  A \emph{contractor} manages a smart contract. Contractors are
  represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
  \TCODE \times \TIME  \times \TBAL \times  \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
  \CODE, \TIME, \BAL, \STORAGE \rangle $ is defined, then $\PUH$ is the
  public hash of a contract,
  $\CODE$ is its  code,
  $\TIME$ is the time when it was accepted,
  $\BAL$ is its current balance,
  and $\STORAGE$ is its current storage.
\end{definition}

@@

  if $\PENDING(\OPH) = \langle  \OP, \TIME, \STATUS
\rangle $ is defined, then $\OPH$ is the public hash of the operation, $\OP$ is the operation, $\TIME$ is the time when the
operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$.
A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge
  \TIME$ and $\OPH = \GENERATEOPH (\OP, \TIME)$.
\end{definition}

@@

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}
\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\EXPRS, \ACCOUNTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall a \in \ACCOUNTS \implies a.\PUK \in \DOM( \MANAGERS)$;
  \end{itemize}
\end{enumerate}
\end{definition}
\begin{definition}
  Preserved by a step on a well-formed configuration $ [\EXPRS, \ACCOUNTS] \|
  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$:
  \todo[inline]{Is this preserved?}
  \begin{itemize}
  \item for all $\OPH$ in $\EXPRS$, $\OPH \in \DOM (\PENDING)$,
  \item for all $\PUK$ in $\EXPRS$, $\PUK \in \DOM (\MANAGERS)$,
  \item for all $\PUH$ in $\EXPRS$, $\PUH \in \DOM (\CONTRACTORS)$.
  \end{itemize}
\end{definition}

@@

\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then
   \begin{itemize}
   \item $\PUK \in \DOM (\MANAGERS)$
  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
  \item $\STRING : \TYPE_s$
  \item if $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).

@@

 \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL,
     \COU}$, then $\BAL \ge \NTEZ +  \MTEZ$ 
\end{itemize}

@@

\begin{mathpar}
  \inferrule[Node-Inject]{
    \Angle{\PAK,\PUK} \in \ACCOUNTS \\
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    %\OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
    \OPH = \GENERATEOPH (\OP, \TIME) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ    
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
     [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     ::\PENDING,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}

@@

The timeout transition applies to all operations.
\begin{mathpar}
  \inferrule[Block-Timeout]{
    % \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME-\hat\TIME > 60
  }{ 
    {[\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
     ::\PENDING, \MANAGERS,
      \CONTRACTORS, \TIME]}
    \BlockTrans \\
    { 
      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
     :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
      \CONTRACTORS, \TIME]}
  }
\end{mathpar}

% \begin{itemize}
% \item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
%   \begin{enumerate}
%   \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
%   \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
%   \end{enumerate}
% \item afterwards must check the status to find whether the
%   transfer is still pending or \TirName{Block-Accept''} or
%   \TirName{Block-Timeout''} has happened.
% \item no further transfer is possible before the status is resolved to
%   accept or timeout.
% \end{itemize}

@@

\begin{mathpar}
  \inferrule[rejected of fee]{
    \NEG\ \CHECKGAS (\BLOCKCHAIN.\MANAGERS, \PUK,\PUK',\NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
     } \SystemTrans
    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
  }
\end{mathpar}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Smart Contracts}
A. Originate

\begin{mathpar}
  \inferrule[Block-Originate]{
   \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKINIT (\CODE, \STRING) \\
    %\OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
    \OPH = \GENERATEOPH(\OP, \TIME) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ    
  }{
    [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     ::\PENDING, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PUH = \GENERATEHASH(\CODE, \TIME) \\
    \TIME-\hat\TIME  \le 60
  }{
      [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \SystemTrans \\
     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
  }
\end{mathpar}

% \begin{mathpar}
%   \inferrule[Block-Timeout]{
%     %\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
%     \TIME-\hat\TIME > 60
% }{
%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
%      ::\PENDING, \MANAGERS,
%       \CONTRACTORS, \TIME]  
%       \BlockTrans \\    
%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
%      :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
%       \CONTRACTORS, \TIME] 
%   }

% \end{mathpar}
~\\
~\\
B. \textbf{Transfer}

\begin{mathpar}
  \inferrule[Block-Call]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\ 
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
%    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
    \OPH = \GENERATEOPH (\OP, \TIME) \\
    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
  }{ [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]     
    \SystemTrans \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
\end{mathpar}

@@

\begin{mathpar}
\inferrule[balance of smart contract]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[storage]{
    \BLOCKSYSTEM = 
      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[code]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[type]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

@@

    \item Function  $\UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER)$ updates the contractor that associates with the public hash $\PUH$, where
    \begin{itemize}
        \item[] $\PUH  \mapsto \langle   \CODE, \TIME, \BAL, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
    \end{itemize}

@@

    \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.

>>>>

\begin{definition}%[Program]
\emph{Expressions} are defined by the following grammar:
\begin{align*}
  \CONSTANT & ::= \ADDR \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\dots) \mid
            \STATUSTIMEOUT \\
  \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
           \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
  \EXPR \mid \SOME\ \EXPR \mid \NONE
  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
  \\&\mid \QOP\  \EXPR\\
  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
\end{align*}
We let $\EXPRS$ range over sets of expressions.

@@

\begin{definition}%[Contractor]
  A \emph{contractor} manages a smart contract. Contractors are
  represented by a partial mapping $\CONTRACTORS : \TPUH \partialto
  \TBAL \times \TCODE \times \TSTORAGE$. If $\CONTRACTORS (\PUH) = \langle
  \BAL, \CODE, \STORAGE \rangle $ is defined, then $\PUH$ is the
  public hash of a contract, $\BAL$ is its current balance, $\CODE$ is its
  code, and $\STORAGE$ is its current storage.
\end{definition}

@@

  if $\PENDING(\OPH) = \langle  \OP, \TIME, \STATUS
\rangle $ is defined, then $\OPH$ is the public hash of the operation, $\OP$ is the operation, $\TIME$ is the time when the
operation was injected, and $\STATUS$ is either $\STATUSPENDING$,
$\STATUSINCLUDED\ \TIME'$, or $\STATUSTIMEOUT$. A pool $\PENDING$ is \emph{well-formed} if, for all $\OPH$, $\PENDING (\OPH) =
  \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$ implies $\TIME' \ge \TIME$.
\end{definition}

@@

\begin{definition}%[Blockchain]
  The \emph{state of a blockchain} is a tuple
  $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a pool of operations, $\MANAGERS$ is a map of managers,
  $\CONTRACTORS$ is a map of contractors, and $\TIME$ is the current
  time. 
\end{definition}
\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\EXPRS, \ACCOUNTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall a \in \ACCOUNTS \implies a.\PUK \in \DOM( \MANAGERS)$;
  \end{itemize}
\end{enumerate}
\end{definition}

@@

\item if $\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ$ and $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then
   \begin{itemize}
   \item $\PUK \in \DOM (\MANAGERS)$
  \item $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
  \item $\STRING : \TYPE_s$
  \item if $\STATUS =
  \STATUSINCLUDED\ \TIME'$, then $\PUH =\GENERATEHASH (\CODE, \INIT, \hat\TIME) \in \DOM (\CONTRACTORS)$ and $\Delta (\PUH)  =\TPAIR\ \TYPE_p\ \TYPE_s$ (or $\CONTRACTORS(\PUH).\CODE = \CODE$).

@@

 \item if $st = \STATUSPENDING$ and $\MANAGERS(\PUK) = \Angle{\BAL, \COU}$, then $\BAL >= \NTEZ +  \MTEZ$
\end{itemize}

@@

\begin{mathpar}
  \inferrule[Node-Inject]{
    \Angle{\PAK,\PUK} \in \ACCOUNTS \\
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OPH = \GENERATEOPH (\PUK, \PUK','', \NTEZ, \MTEZ, \TIME) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ    
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
     [ \OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     ::\PENDING,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME-\hat\TIME > 60
  }{ 
    {[\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSPENDING}
     ::\PENDING, \MANAGERS,
      \CONTRACTORS, \TIME]}
    \BlockTrans \\
    { 
      [\OPH \mapsto \Angle{\OP, \hat \TIME, \STATUSTIMEOUT}
     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME]}
  }
\end{mathpar}

\begin{itemize}
\item library call \texttt{call\_contract} with \texttt{confirmations:None} corresponds to
  \begin{enumerate}
  \item{} first \TirName{Node-Op'}, \TirName{Node-Inject'}
  \item{} first \TirName{Node-Op'}, \TirName{Node-Reject(balance,count,pubkey,fee)}
  \end{enumerate}
\item afterwards must check the status to find whether the
  transfer is still pending or \TirName{Block-Accept''} or
  \TirName{Block-Timeout''} has happened.
\item no further transfer is possible before the status is resolved to
  accept or timeout.
\end{itemize}

@@

\begin{mathpar}
  \inferrule[rejected of fee]{
    \NEG\ \CHECKGAS (\BLOCKCHAIN.\MANAGERS, \PUK,\PUK',\NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
     } \SystemTrans
    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
  }
\end{mathpar}
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
\subsection{Smart Contracts}
A. Originate

\begin{mathpar}
  \inferrule[Block-Originate]{
   \Angle{\PAK,\PUK} \in \ACCOUNTS \\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKINIT (\CODE, \STRING) \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \STRING, \NTEZ, \MTEZ, \TIME) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ    
  }{
    [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     ::\PENDING, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PUH = \GENERATEHASH(\CODE, \INIT, \TIME) \\
    \TIME-\hat\TIME  \le 60
  }{
      [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \SystemTrans \\
     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME+1]
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME-\hat\TIME > 60
}{
      [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
     ::\PENDING, \MANAGERS,
      \CONTRACTORS, \TIME]  
      \BlockTrans \\    
      [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME] 
  }

\end{mathpar}
~\\
~\\
B. \textbf{Transfer}

\begin{mathpar}
  \inferrule[Block-Call]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\ 
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
  }{ [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]     
    \SystemTrans \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
\end{mathpar}

@@

\begin{mathpar}
\inferrule[balance of smart contract]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[storage]{
    \BLOCKSYSTEM = 
      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[code]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[type]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\BAL, \CODE, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \NodeTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

@@

    \item Function  $\UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER)$ updates the contractor that associates with the public hash $\PUH$, where
    \begin{itemize}
        \item[] $\PUH  \mapsto \langle   \BAL, \CODE, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
    \end{itemize}

@@

    \item Function \GENERATEHASH (\CODE, \INIT, \TIME)  generates the public hash of a smart contract.
